Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-24 notes/fullproof/main.tex
update proofs

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}

\maketitle
\section{Preliminaries}
\label{sec_background}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

\section{Technical Problem Statement and Motivations}
\label{sec_moti}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\sim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(x)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\displaystyle\sum_{r\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}
where $S_\beta(x)$ is the smooth sensitivity of $\hellinger(\bysinfer(x),-)$, calculated by:

@@

The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.\\

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
Given $\hexpmech(x)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta)$, $\epsilon\geq 0$ and $|\delta| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] + \frac{\delta}{2},
\end{equation*}

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]$ for the utility score for $r$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance. More specifically, for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff $\alpha_2 = \beta_1$,  $\alpha_1 = \beta_2$ and $\alpha_0 + \alpha_1 = \beta_0 + \beta_2$ and $\alpha_0 + \alpha_2 = \beta_0 + \beta_1$.

 From this, we can derive that there are either only one or two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$ we have: $
 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ either 
 $$
 =\frac{1}{2}\Big (\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) =
 \hellinger(\bysinfer(x),r)]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(x)}{Pr}[\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)]
 $$
 % proportional too $\hellinger(\bysinfer(x),r)$, i.e., $u(x,z)$. We can derive, if $u(r,x) = u(r',x)$ then $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[z = r']$. 
 We assume the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(x),z) = \hellinger(\bysinfer(x),r)$, i.e. $u(z,x) = u(r,x)$ is $|z|$, then  $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = |z| \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$. It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r]$.

 The same way in Dirichlet-multinomial system. By combination and permutation, $|z|$ can take value of 1 or 3 or 6 in 3 dimensionality, and trivially in higher dimensions.

@@

		We denote the normalizer of the probability mass in $\hexpmech(x)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(x)})$ as $NL(x)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{r \thicksim \hexpmech(x)}{Pr}[u(r,x) = \hat{s}]
		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(x)})}{NL(x)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta - \Delta)}{2 S(x)})}{NL(x)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)} + \frac{- \epsilon \Delta}{2 S(x)})}{NL(x)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)})}.\\
		\end{split}
		\end{equation*}

		By bounding the $\Delta \geq -S(x)$, we can get:

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{- \epsilon \Delta}{2 S(x)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \Delta)}{2 S(x)})}{NL(x)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(r,x) = (\Delta + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
for any exponential mechanism $\hexpmech(x)$, $\lambda < |\beta|$, $\epsilon$, $|\delta| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
We partition $\candidateset$ in the same way as before, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(x)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(x)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(x)) (1 - e^{\lambda})}{S(x)})$. Consider the event $G = \{ \hexpmech(x) : u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta}{2}$.\\

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(x)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta}{2}
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(x)) = c] = \frac{exp(\frac{\epsilon c}{2 S(x)})}{NL(x)}$ and $Pr[u(\hexpmech(x)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(x)})}{NL(x)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(x),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(x)$, we can substitute $\hat{s}$ with $u(\hexpmech(x))$. Then, what we need to proof under the case $\lambda > 0$ is:
		\begin{equation}
		\label{eq_dilation_case2}
		u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}
		\end{equation}
		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(x)}}{2 GS})}\\
		\end{split}
		\end{equation*}

		we derived the accuracy bound for $\hexpmech$:

		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(x)) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(x)})
		\end{split}
		\end{equation*}

		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(x)}{(1 - e ^ {\lambda})}/2 S(x))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})})\\
		\end{split}
		\end{equation*}

		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(x)) \leq \frac{S(x)}{(1 - e ^ {\lambda})}] \leq \frac{\delta}{2}$.

		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.

@@

	Given that $\underset{z \thicksim \hexpmech(x)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(x)}{Pr}[u(x,z) = u(x,r)]$, let $U = u(x,r)$, $U_1 = u(y,z) - u(x,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(x)}{S(y)} \cdot \ln(\frac{NL(x)}{NL(y)})$. Then,

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
\section{Preliminaries}
\label{sec_background}

@@

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

\section{Technical Problem Statement and Motivations}
\label{sec_moti}
We are interested in designing a mechanism for privately releasing the full posterior
distributions derived in section \ref{sec_background}, as opposed to just sampling from them.
It's worth noticing that the posterior distributions are fully characterized
by their parameters, and the family (beta, Dirichlet) they belong to. Hence, in case of the
Beta-Binomial model we are interested in releasing a private version of the pair of
parameters $(\alpha',\beta')=(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)$, and
in the case of the Dirichlet-multinomial model we are interested in a private version of
$\valpha'=(\valpha + \Delta \valpha)$. \cite{zhang2016differential} and \cite{xiao2012bayesian}
have already attacked this problem by adding independent Laplacian noise to the
parameters of the posteriors. That is, in the case of the Beta-Binomial system,
the value released would  be: $(\tilde\alpha,\tilde\beta)=(\alpha +  \widetilde{\Delta \alpha},\beta + n - \widetilde{\Delta \alpha})$
where $\widetilde{\Delta \alpha}\thicksim \lap{\Delta \alpha}{\frac{2}{\epsilon}}$,
and where $\lap{\mu}{\nu}$ denotes a Laplace random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t. to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent data observations $\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system. Details are introduced in Sec. \ref{subsec_baselines}.

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

@@

The differential privacy property of $\hexpmech$ is proved based on following two lemmas: Lemma \ref{lem_sliding} and Lemma \ref{lem_dilation}.\\

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

@@

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
 \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.

 \begin{thm}
 \label{thm_hellinegr_equality_beta}
 for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
  $$
  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2, \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
  $$
 \end{thm}

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
  $$
  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
 \end{thm}

 \begin{thm}
 \label{thm_candidate_divide}
 There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either 
 $$
 = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
 $$
 \end{thm}
 \begin{proof} of Theorem \ref{thm_candidate_divide}.

 Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 \end{proof}

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
 \end{proof}

@@

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

		By bounding the $\delta' \geq -S(\dataobs)$, we can get:

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

@@

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$. Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.

	After simplification, we need to show: $u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}$.
	Because the sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,x) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

@@

		The left hand side will always be smaller than 0 and the right hand side greater than 0. This will always holds, i.e.
		\begin{equation*}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}
		\end{equation*}
		is always true when $\lambda < 0$
	\item $\lambda > 0$

		Because $\hat{s} = u(r)$ where $r \thicksim \hexpmech(\dataobs)$, we can substitute $\hat{s}$ with $u(\hexpmech(\dataobs))$. Then, what we need to proof under the case $\lambda > 0$ is:
		\begin{equation}
		\label{eq_dilation_case2}
		u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}.
		\end{equation}

		Based on the accuracy property of exponential mechanism:
		\begin{equation*}
		\begin{split}
		Pr[u(\expmech{}{x}{u}{\candidateset}) \leq c] 
		& \leq \frac{|\mathcal{R}|exp(\frac{\epsilon c}{2 GS})}{|\mathcal{R}_{OPT}| exp(\frac{\epsilon OPT_{u(\dataobs)}}{2 GS})},\\
		\end{split}
		\end{equation*}
		we derived the accuracy bound for $\hexpmech$:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq c] 
		& \leq |\candidateset|exp(\frac{\epsilon c}{2 S(\dataobs)}).
		\end{split}
		\end{equation*}

		In Beta-binomial system, $|\candidateset| = n + 1$, apply this bound to eq. \ref{eq_dilation_case2}:
		\begin{equation*}
		\begin{split}
		Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] 
		& = (n + 1)exp(\frac{\epsilon S(\dataobs)}{(1 - e ^ {\lambda})}/2 S(\dataobs))\\
		& = (n + 1)exp(\frac{\epsilon}{2 (1 - e ^ {\lambda})}).\\
		\end{split}
		\end{equation*}

		When we set $\lambda \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, it is easily to derive that $Pr[u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e ^ {\lambda})}] \leq \frac{\delta'}{2}$.

		In Dirichlet-multinomial system, $\lambda$ is set as $ \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ since $|\candidateset| \neq n + 1$ any more.

@@

	Given that $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r] = \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(\dataobs,z) = u(\dataobs,r)]$, let $U = u(\dataobs,r)$, $U_1 = u(\dataobs',z) - u(\dataobs,z)$, $U_2 = U + U_1$ and $U_3 = U_2 \cdot \frac{S(\dataobs)}{S(\dataobs')} \cdot \ln(\frac{NL(\dataobs)}{NL(\dataobs')})$. Then,
